What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-07 presentation/proposal_pres.Rmd
last minute updates to slides and proposal

The package `shiny` allows us to build web apps using R's capabilities in the background
We can add interactive inputs to visualisations.

An example of what we can make:

>>>>

The package `shiny` allows us to build web apps using R's capabilities in the background

We can add interactive inputs to visualisations

#### An example of what we can make:

### 2017-05-07 thesis/proposal_draft.Rmd
last minute updates to slides and proposal

---
title: "What can we learn about life in the city by mining the Melbourne’s Open Data Platform?"
subtitle: "Thesis Proposal"
date: April 2017
author: 
- "Gavin Chin"
- "supervised by Dianne Cook"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
---

>>>>

---
title: "What can we learn about life in the city by mining the Melbourne’s Open Data Platform?"
subtitle: "Thesis Proposal"
date: 7 May 2017
author: 
- "Gavin Chin"
- "supervised by Dianne Cook"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
---
